Packaging research artefacts with RO-Crate

### 2022-01-02 latex/ro-crate.tex
minor typos
bibliography fixes

A mapping has been produced between Research Object Crates and
Machine-actionable Data Management Plans
\cite{doi:10.4126/frl01-006423291}, implemented by the RO-Crate RDA maDMP
Mapper \cite{doi:10.5281/zenodo.3922136}. A similar mapping has been
implemented by \texttt{RO-Crate\_2\_ma-DMP} \cite{doi:10.5281/zenodo.3903463}. In
both cases, a maDMP can be converted to a RO-Crate, or vice versa. In
\cite{doi:10.4126/frl01-006423291} this functionality caters for two use cases:
\begin{enumerate}
\item[1.] Start a skeleton data management plan based on an existing RO-Crate
dataset, e.g. an RO-Crate from WorkflowHub.
\item[2.] Instantiate an RO-Crate based on a data management plan.
\end{enumerate}

@@

The below is an example RO-Crate represented using the above
formalisation, assuming a base IRI of \texttt{<http://example.com/ro/123/>}:
%
{\fontsize{9.7}{11.7}\selectfont{\begin{gather*}
\textit{ROCrate}(\texttt{<http://example.com/ro/123/>})
\\
\textit{name}\bigl(\texttt{<http://example.com/ro/123/>},
\\
\quad \text{``Data files associated with the manuscript:Effects of {
\ldots}''}\bigr)
\\
\textit{description}\bigl(\texttt{<http://example.com/ro/123/>},
\\
\quad \text{``Palliative care planning for nursing home residents {
\ldots}''}\bigr)
\\
\textit{license}(\texttt{<http://example.com/ro/123/>},
\\
\quad \texttt{<https://spdx.org/licenses/CC-BY-4.0>})
\\
\textit{datePublished}\bigl(\texttt{<http://example.com/ro/123/>}, \text
{``2017-02-23''}\bigr)
\\
\textit{hasPart}(\texttt{<http://example.com/ro/123/>}, \texttt{<http://example.com/ro/123/file.txt>})
\\
\textit{hasPart}(\texttt{<http://example.com/ro/123/>}, \texttt{<http://example.com/ro/123/interviews/>})
\\
\\
\textit{ContextualEntity}(\texttt{<https://spdx.org/licenses/CC-BY-4.0>})
\\
\textit{name}\bigl(\texttt{<https://spdx.org/licenses/CC-BY-4.0>},
\\
\quad \text{Creative Commons Attribution 4.0''}\bigr)
\\
\\
\textit{ContextualEntity}(\texttt{<https://spdx.org/licenses/CC-BY-NC-4.0>})
\\
\textit{name}\bigl(\texttt{<https://spdx.org/licenses/CC-BY-NC-4.0>},
\\
\quad \text{Creative Commons Attribution Non Commercial 4.0''}
\bigr)
\\
\\
\textit{File}(\texttt{<http://example.com/ro/123/survey.csv>})
\\
\textit{name}\bigl(\texttt{<http://example.com/ro/123/survey.csv>},
\text{``Survey of care providers''}\bigr)
\\
\\
\textit{Dataset}(\texttt{<http://example.com/ro/123/interviews/>})
\\
\textit{name}\bigl(\texttt{<http://example.com/ro/123/interviews/>},
\\
\quad \text{``Audio recordings of care provider interviews''}
\bigr)
\\
\textit{license}(\texttt{<http://example.com/ro/123/interviews/>},
\\*
\quad \texttt{<https://spdx.org/licenses/CC-BY-NC-4.0>})
\end{gather*}}}

@@

Combining the above predicates and Schema.org mapping with rudimentary
JSON templates, these forward-chaining production rules can output
JSON-LD according to the RO-Crate 1.1 specification:\footnote{\textbf{Limitations:}
 Contextual entities not related from the
RO-Crate (e.g. using inverse relations to a data entity) would not be
covered by the single direction $Mentions(R, s)$ production rule; see
\href{https://github.com/ResearchObject/ro-crate/issues/122}{GitHub
issue ResearchObject/ro-crate\#122}. The $\textit{datePublished}(e, d)$ rule do
not include syntax checks for the ISO 8601 datetime format. Compared
with RO-Crate examples, this generated JSON-LD does not use a
$\textit{@context}$ as the IRIs are produced unshortened, a post-step could do
JSON-LD Flattening with a versioned RO-Crate context. The \texttt
{@type} expansion is included for clarity, even though this is also
implied by the $\textit{type}(e, t)$ expansion to $\textit{Relation}(e, \texttt{xsd:type})$.}
%
\begin{eqnarray*}
\textit{Mentions}(R, s) \land \textit{Relation}(s,p,o) & \Rightarrow&
\textit{Mentions}(R, o)
\\
\textit{IRI}(i) & \Rightarrow& \texttt{"} i \texttt{"}
\\
\textit{Decimal}(d) & \Rightarrow& d
\\
\textit{String}(s) & \Rightarrow& \texttt{"} s \texttt{"}
\\
\forall e \forall t \ \textit{type}(e, t) & \Rightarrow& \texttt{\{"@id":} e
\texttt{,}
\\
&& \ \ \texttt{"@type":} t
\\
&& \texttt{\}}
\\
\forall s \forall p \forall o \ \textit{Relation}(s,p,o) & \Rightarrow& 
\texttt{\{"@id":} s \texttt{,}
\\
&& \ \ p \texttt{: \{"@id":} o \texttt{\}}
\\
&& \texttt{\}}
\\
\forall s \forall p \forall v \ \textit{Attribute}(s,p,v) & \Rightarrow&
\texttt{\{"@id":} s \texttt{,}
\\
&& \ \ p \texttt{:} v
\\
&& \texttt{\}}
\\
\forall r \forall c\ \textit{ROCrate}(r) & \Rightarrow& \texttt{\{
"@graph": [}
\\
&& \ \ \ \ \ \ \textit{Mentions}(r, c)*
\\
&& \ \ \ \texttt{]}
\\
&& \texttt{\}}
\\
R & \equiv& \texttt{<./>}
\\
R & \Rightarrow& \textit{MetadataFile}(\texttt{<ro-crate-metadata.json>})
\end{eqnarray*}

@@

%b5 ###bbsrt2
%b77 ###
\bibitem{doi:10.1371/journal.pbio.3000099}
%
\begin{barticle}
\bauthor{\binits{G.}~\bsnm{Alterovitz}},
\bauthor{\binits{D.}~\bsnm{Dean}},
\bauthor{\binits{C.}~\bsnm{Goble}},
\bauthor{\binits{M.R.}~\bsnm{Crusoe}},
\bauthor{\binits{S.}~\bsnm{Soiland-Reyes}},
\bauthor{\binits{A.}~\bsnm{Bell}},
\bauthor{\binits{A.}~\bsnm{Hayes}},
\bauthor{\binits{A.}~\bsnm{Suresh}},
\bauthor{\binits{A.}~\bsnm{Purkayastha}},
\bauthor{\binits{C.H.}~\bsnm{King}},
\bauthor{\binits{D.}~\bsnm{Taylor}},
\bauthor{\binits{E.}~\bsnm{Johanson}},
\bauthor{\binits{E.E.}~\bsnm{Thompson}},
\bauthor{\binits{E.}~\bsnm{Donaldson}},
\bauthor{\binits{H.}~\bsnm{Morizono}},
\bauthor{\binits{H.}~\bsnm{Tsang}},
\bauthor{\binits{J.K.}~\bsnm{Vora}},
\bauthor{\binits{J.}~\bsnm{Goecks}},
\bauthor{\binits{J.}~\bsnm{Yao}},
\bauthor{\binits{J.S.}~\bsnm{Almeida}},
\bauthor{\binits{J.}~\bsnm{Keeney}},
\bauthor{\binits{K.}~\bsnm{Addepalli}},
\bauthor{\binits{K.}~\bsnm{Krampis}},
\bauthor{\binits{K.M.}~\bsnm{Smith}},
\bauthor{\binits{L.}~\bsnm{Guo}},
\bauthor{\binits{M.}~\bsnm{Walderhaug}},
\bauthor{\binits{M.}~\bsnm{Schito}},
\bauthor{\binits{M.}~\bsnm{Ezewudo}},
\bauthor{\binits{N.}~\bsnm{Guimera}},
\bauthor{\binits{P.}~\bsnm{Walsh}},
\bauthor{\binits{R.}~\bsnm{Kahsay}},
\bauthor{\binits{S.}~\bsnm{Gottipati}},
\bauthor{\binits{T.C.}~\bsnm{Rodwell}},
\bauthor{\binits{T.}~\bsnm{Bloom}},
\bauthor{\binits{Y.}~\bsnm{Lai}},
\bauthor{\binits{V.}~\bsnm{Simonyan}} and
\bauthor{\binits{R.}~\bsnm{Mazumder}},
\batitle{Enabling precision medicine via standard communication of {HTS}
provenance, analysis, and results},
\bjtitle{PLoS Biology}
\bvolume{16}(\bissue{12})
(\byear{2018}),
\bnumber{e3000099}.
\bid{doi={10.1371/journal.pbio.3000099}}
\end{barticle}
%
\OrigBibText
G.~Alterovitz,
D.~Dean,
C.~Goble,
M.R.~Crusoe,
S.~Soiland-Reyes,
A.~Bell,
A.~Hayes,
A.~Suresh,
A.~Purkayastha,
C.H.~King,
D.~Taylor,
E.~Johanson,
E.E.~Thompson,
E.~Donaldson,
H.~Morizono,
H.~Tsang,
J.K.~Vora,
J.~Goecks,
J.~Yao,
J.S.~Almeida,
J.~Keeney,
K.~Addepalli,
K.~Krampis,
K.M.~Smith,
L.~Guo,
M.~Walderhaug,
M.~Schito,
M.~Ezewudo,
N.~Guimera,
P.~Walsh,
R.~Kahsay,
S.~Gottipati,
T.C.~Rodwell,
T.~Bloom,
Y.~Lai,
V.~Simonyan and
R.~Mazumder,
\textit{Enabling precision medicine via standard communication of {HTS}
provenance, analysis, and results.},
{PLoS} Biology
16(12)
(2018),
e3000099.
doi:10.1371/journal.pbio.3000099.
\endOrigBibText
\bptok{structpyb}
\endbibitem

@@

%b10 ###bbsrt2
%b64 ###
\bibitem{doi:10.1371/journal.ppat.1008643}
%
\begin{barticle}
\bauthor{\binits{D.}~\bsnm{Baker}},
\bauthor{\binits{M.}~\bsnm{van den Beek}},
\bauthor{\binits{D.}~\bsnm{Blankenberg}},
\bauthor{\binits{D.}~\bsnm{Bouvier}},
\bauthor{\binits{J.}~\bsnm{Chilton}},
\bauthor{\binits{N.}~\bsnm{Coraor}},
\bauthor{\binits{F.}~\bsnm{Coppens}},
\bauthor{\binits{I.}~\bsnm{Eguinoa}},
\bauthor{\binits{S.}~\bsnm{Gladman}},
\bauthor{\binits{B.}~\bsnm{Gr\"{u}ning}},
\bauthor{\binits{N.}~\bsnm{Keener}},
\bauthor{\binits{D.}~\bsnm{Larivi\`{e}re}},
\bauthor{\binits{A.}~\bsnm{Lonie}},
\bauthor{\binits{S.}~\bsnm{Kosakovsky Pond}},
\bauthor{\binits{W.}~\bsnm{Maier}},
\bauthor{\binits{A.}~\bsnm{Nekrutenko}},
\bauthor{\binits{J.}~\bsnm{Taylor}} and
\bauthor{\binits{S.}~\bsnm{Weaver}},
\batitle{No more business as usual: Agile and effective responses to emerging
pathogen threats require open data and open analytics},
\bjtitle{PLoS Pathogens}
\bvolume{16}(\bissue{8})
(\byear{2020}),
\bnumber{e1008643}.
\bid{doi={10.1371/journal.ppat.1008643}}
\end{barticle}
%
\OrigBibText
D.~Baker,
M.~van~den Beek,
D.~Blankenberg,
D.~Bouvier,
J.~Chilton,
N.~Coraor,
F.~Coppens,
I.~Eguinoa,
S.~Gladman,
B.~Gr\"{u}ning,
N.~Keener,
D.~Larivi\`{e}re,
A.~Lonie,
S.~Kosakovsky~Pond,
W.~Maier,
A.~Nekrutenko,
J.~Taylor and
S.~Weaver,
\textit{No more business as usual: Agile and effective responses to emerging
pathogen threats require open data and open analytics.},
{PLoS} Pathogens
16(8)
(2020),
e1008643.
doi:10.1371/journal.ppat.1008643.
\endOrigBibText
\bptok{structpyb}
\endbibitem

%b11 ###bbsrt2
%b89 ###
\bibitem{doi:10.5334/dsj-2019-044}
%
\begin{barticle}
\bauthor{\binits{M.}~\bsnm{Barker}},
\bauthor{\binits{R.}~\bsnm{Wilkinson}} and
\bauthor{\binits{A.}~\bsnm{Treloar}},
\batitle{The Australian research data commons},
\bjtitle{Data Science Journal}
\bvolume{18}
(\byear{2019}).
\bid{doi={10.5334/dsj-2019-044}}
\end{barticle}
%
\OrigBibText
M.~Barker,
R.~Wilkinson and
A.~Treloar,
The Australian Research Data Commons,
\textit{Data Science Journal}
\textbf{18}
(2019), 00.
doi:10.5334/dsj-2019-044.
\endOrigBibText
\bptok{structpyb}
\endbibitem

@@

%b14 ###bbsrt2
%b12 ###
\bibitem{doi:10.1016/j.websem.2015.01.003}
%
\begin{barticle}
\bauthor{\binits{K.}~\bsnm{Belhajjame}},
\bauthor{\binits{J.}~\bsnm{Zhao}},
\bauthor{\binits{D.}~\bsnm{Garijo}},
\bauthor{\binits{M.}~\bsnm{Gamble}},
\bauthor{\binits{K.}~\bsnm{Hettne}},
\bauthor{\binits{R.}~\bsnm{Palma}},
\bauthor{\binits{E.}~\bsnm{Mina}},
\bauthor{\binits{O.}~\bsnm{Corcho}},
\bauthor{\binits{J.M.}~\bsnm{G\'{o}mez-P\'{e}rez}},
\bauthor{\binits{S.}~\bsnm{Bechhofer}},
\bauthor{\binits{G.}~\bsnm{Klyne}} and
\bauthor{\binits{C.}~\bsnm{Goble}},
\batitle{Using a suite of ontologies for preserving workflow-centric
research objects},
\bjtitle{Web Semantics: Science, Services and Agents on the World Wide Web}
\bvolume{32}(\bissue{0})
(\byear{2015}),
\bfpage{16}--\blpage{42}.
\bid{doi={10.1016/j.websem.2015.01.003}}
\end{barticle}
%
\OrigBibText
K.~Belhajjame,
J.~Zhao,
D.~Garijo,
M.~Gamble,
K.~Hettne,
R.~Palma,
E.~Mina,
O.~Corcho,
J.M.~G\'{o}mez-P\'{e}rez,
S.~Bechhofer,
G.~Klyne and
C.~Goble,
\textit{Using a suite of ontologies for preserving workflow-centric research
objects},
Web Semantics: Science, Services and Agents on the World Wide Web
32(0)
(2015),
16--42.
doi:10.1016/j.websem.2015.01.003.
\endOrigBibText
\bptok{structpyb}
\endbibitem

@@

%b32 ###bbsrt2
%b92 ###
\bibitem{doi:10.1045/january2011-crosas}
%
\begin{barticle}
\bauthor{\binits{M.}~\bsnm{Crosas}},
\batitle{The dataverse network: An open-source application for sharing,
discovering and preserving data},
\bjtitle{D-Lib Magazine}
\bvolume{17}(\bissue{1/2})
(\byear{2011}).
\bid{doi={10.1045/january2011-crosas}}
\end{barticle}
%
\OrigBibText
M.~Crosas,
The Dataverse Network: An Open-Source Application for Sharing,
Discovering and
Preserving Data,
\textit{D-Lib Magazine}
\textbf{17}(1/2)
(2011)
00.
doi:10.1045/january2011-crosas.
\endOrigBibText
\bptok{structpyb}
\endbibitem

@@

%b36 ###bbsrt2
%b69 ###
\bibitem{doi:10.1145/3486897}
%
\begin{bbook}
\bauthor{\binits{M.R.}~\bsnm{Crusoe}},
\bauthor{\binits{S.}~\bsnm{Abeln}},
\bauthor{\binits{A.}~\bsnm{Iosup}},
\bauthor{\binits{P.}~\bsnm{Amstutz}},
\bauthor{\binits{J.}~\bsnm{Chilton}},
\bauthor{\binits{N.}~\bsnm{Tijani\'{c}}},
\bauthor{\binits{H.}~\bsnm{M\'{e}nager}},
\bauthor{\binits{S.}~\bsnm{Soiland-Reyes}} and
\bauthor{\binits{C.}~\bsnm{Goble}},
\bbtitle{Methods Included: Standardizing Computational Reuse and Portability
with the Common Workflow Language},
\bpublisher{Communications of the ACM},
\byear{2021}.
\bcomment{Accepted}.
\bid{doi={10.1145/3486897}}
\end{bbook}
%
\OrigBibText
M.R.~Crusoe,
S.~Abeln,
A.~Iosup,
P.~Amstutz,
J.~Chilton,
N.~Tijani\'{c},
H.~M\'{e}nager,
S.~Soiland-Reyes and
C.~Goble,
\textit{Methods Included: Standardizing Computational Reuse and Portability
with the Common Workflow Language},
Communications of the ACM
(2021),
Accepted.
doi:10.1145/3486897.
\endOrigBibText
\bptok{structpyb}
\endbibitem

@@

%b91 ###bbsrt2
%b6 ###
\bibitem{isbn:9781315351148}
%
\begin{botherref}
\oauthor{\binits{B.}~\bsnm{Mons}},
Data Stewardship for Open Science,
1st edn,
Taylor \& Francis,
p.~240.
ISBN 9781315351148.
\end{botherref}
%
\OrigBibText
B.~Mons,
\textit{Data Stewardship for Open Science},
1st edn,
Taylor \& Francis,
p.~240.
ISBN 9781315351148.
\endOrigBibText
\bptok{structpyb}
\endbibitem

>>>>

A mapping has been produced between Research Object Crates and
Machine-actionable Data Management Plans
\cite{doi:10.4126/frl01-006423291}, implemented by the RO-Crate RDA maDMP
Mapper \cite{doi:10.5281/zenodo.3922136}. A similar mapping has been
implemented by \textit{RO-Crate\_2\_ma-DMP} \cite{doi:10.5281/zenodo.3903463}. In
both cases, a maDMP can be converted to a RO-Crate, or vice versa. In
\cite{doi:10.4126/frl01-006423291} this functionality caters for two use cases:
\begin{enumerate}
\item[1.] Start a skeleton data management plan based on an existing RO-Crate
dataset, e.g. an RO-Crate from WorkflowHub.
\item[2.] Instantiate an RO-Crate based on a data management plan.
\end{enumerate}

@@

The below is an example RO-Crate represented using the above
formalisation, assuming a base IRI of \texttt{<http://example.com/ro/123/>}:
%
{\fontsize{9.7}{11.7}\selectfont{\begin{gather*}
\textit{ROCrate}(\texttt{<http://example.com/ro/123/>})
\\
\textit{name}\bigl(\texttt{<http://example.com/ro/123/>},
\\
\quad \text{``Data files associated with the manuscript:Effects of {
\ldots}''}\bigr)
\\
\textit{description}\bigl(\texttt{<http://example.com/ro/123/>},
\\
\quad \text{``Palliative care planning for nursing home residents {
\ldots}''}\bigr)
\\
\textit{license}(\texttt{<http://example.com/ro/123/>},
\\
\quad \texttt{<https://spdx.org/licenses/CC-BY-4.0>})
\\
\textit{datePublished}\bigl(\texttt{<http://example.com/ro/123/>}, \text
{``2017-02-23''}\bigr)
\\
\textit{hasPart}(\texttt{<http://example.com/ro/123/>}, \texttt{<http://example.com/ro/123/file.txt>})
\\
\textit{hasPart}(\texttt{<http://example.com/ro/123/>}, \texttt{<http://example.com/ro/123/interviews/>})
\\
\\
\textit{ContextualEntity}(\texttt{<https://spdx.org/licenses/CC-BY-4.0>})
\\
\textit{name}\bigl(\texttt{<https://spdx.org/licenses/CC-BY-4.0>},
\\
\quad \text{``Creative Commons Attribution 4.0''}\bigr)
\\
\\
\textit{ContextualEntity}(\texttt{<https://spdx.org/licenses/CC-BY-NC-4.0>})
\\
\textit{name}\bigl(\texttt{<https://spdx.org/licenses/CC-BY-NC-4.0>},
\\
\quad \text{``Creative Commons Attribution Non Commercial 4.0''}
\bigr)
\\
\\
\textit{File}(\texttt{<http://example.com/ro/123/survey.csv>})
\\
\textit{name}\bigl(\texttt{<http://example.com/ro/123/survey.csv>},
\text{``Survey of care providers''}\bigr)
\\
\\
\textit{Dataset}(\texttt{<http://example.com/ro/123/interviews/>})
\\
\textit{name}\bigl(\texttt{<http://example.com/ro/123/interviews/>},
\\
\quad \text{``Audio recordings of care provider interviews''}
\bigr)
\\
\textit{license}(\texttt{<http://example.com/ro/123/interviews/>},
\\*
\quad \texttt{<https://spdx.org/licenses/CC-BY-NC-4.0>})
\end{gather*}}}

@@

Combining the above predicates and Schema.org mapping with rudimentary
JSON templates, these forward-chaining production rules can output
JSON-LD according to the RO-Crate 1.1 specification:\footnote{\textbf{Limitations:}
 Contextual entities not related from the
RO-Crate (e.g. using inverse relations to a data entity) would not be
covered by the single direction $Mentions(R, s)$ production rule; see
\href{https://github.com/ResearchObject/ro-crate/issues/122}{GitHub
issue ResearchObject/ro-crate\#122}. The $\textit{datePublished}(e, d)$ rule do
not include syntax checks for the ISO 8601 datetime format. Compared
with RO-Crate examples, this generated JSON-LD does not use a
$\textit{@context}$ as the IRIs are produced unshortened, a post-step could do
JSON-LD Flattening with a versioned RO-Crate context. The \texttt
{@type} expansion is included for clarity, even though this is also
implied by the $\textit{type}(e, t)$ expansion to $\textit{Relation}(e, \texttt{xsd:type})$.}
%
\begin{eqnarray*}
\textit{Mentions}(R, s) \land \textit{Relation}(s,p,o) & \Rightarrow&
\textit{Mentions}(R, o)
\\
\textit{IRI}(i) & \Rightarrow& \texttt{"} i \texttt{"}
\\
\textit{Decimal}(d) & \Rightarrow& d
\\
\textit{String}(s) & \Rightarrow& \texttt{"} s \texttt{"}
\\
\forall e \forall t \ \textit{type}(e, t) & \Rightarrow& \texttt{\{"@id":} e
\texttt{,}
\\
&& \ \ \texttt{"@type":} t
\\
&& \texttt{\}}
\\
\forall s \forall p \forall o \ \textit{Relation}(s,p,o) & \Rightarrow& 
\texttt{\{"@id":} s \texttt{,}
\\
&& \ \ p \texttt{: \{"@id":} o \texttt{\}}
\\
&& \texttt{\}}
\\
\forall s \forall p \forall v \ \textit{Attribute}(s,p,v) & \Rightarrow&
\texttt{\{"@id":} s \texttt{,}
\\
&& \ \ p \texttt{:} v
\\
&& \texttt{\}}
\\
\forall r \forall c\ \textit{ROCrate}(r) & \Rightarrow& 
\texttt{\{"@graph": [}
\\
&& \ \ \ \ \ \ \textit{Mentions}(r, c)*
\\
&& \ \ \ \texttt{]}
\\
&& \texttt{\}}
\\
R & \equiv& \texttt{<./>}
\\
R & \Rightarrow& \textit{MetadataFile}(\texttt{<ro-crate-metadata.json>})
\end{eqnarray*}

@@

%b5 ###bbsrt2
%b77 ###
\bibitem{doi:10.1371/journal.pbio.3000099}
%
\begin{barticle}
\bauthor{\binits{G.}~\bsnm{Alterovitz}},
\bauthor{\binits{D.}~\bsnm{Dean}},
\bauthor{\binits{C.}~\bsnm{Goble}},
\bauthor{\binits{M.R.}~\bsnm{Crusoe}},
\bauthor{\binits{S.}~\bsnm{Soiland-Reyes}},
\bauthor{\binits{A.}~\bsnm{Bell}},
\bauthor{\binits{A.}~\bsnm{Hayes}},
\bauthor{\binits{A.}~\bsnm{Suresh}},
\bauthor{\binits{A.}~\bsnm{Purkayastha}},
\bauthor{\binits{C.H.}~\bsnm{King}},
\bauthor{\binits{D.}~\bsnm{Taylor}},
\bauthor{\binits{E.}~\bsnm{Johanson}},
\bauthor{\binits{E.E.}~\bsnm{Thompson}},
\bauthor{\binits{E.}~\bsnm{Donaldson}},
\bauthor{\binits{H.}~\bsnm{Morizono}},
\bauthor{\binits{H.}~\bsnm{Tsang}},
\bauthor{\binits{J.K.}~\bsnm{Vora}},
\bauthor{\binits{J.}~\bsnm{Goecks}},
\bauthor{\binits{J.}~\bsnm{Yao}},
\bauthor{\binits{J.S.}~\bsnm{Almeida}},
\bauthor{\binits{J.}~\bsnm{Keeney}},
\bauthor{\binits{K.}~\bsnm{Addepalli}},
\bauthor{\binits{K.}~\bsnm{Krampis}},
\bauthor{\binits{K.M.}~\bsnm{Smith}},
\bauthor{\binits{L.}~\bsnm{Guo}},
\bauthor{\binits{M.}~\bsnm{Walderhaug}},
\bauthor{\binits{M.}~\bsnm{Schito}},
\bauthor{\binits{M.}~\bsnm{Ezewudo}},
\bauthor{\binits{N.}~\bsnm{Guimera}},
\bauthor{\binits{P.}~\bsnm{Walsh}},
\bauthor{\binits{R.}~\bsnm{Kahsay}},
\bauthor{\binits{S.}~\bsnm{Gottipati}},
\bauthor{\binits{T.C.}~\bsnm{Rodwell}},
\bauthor{\binits{T.}~\bsnm{Bloom}},
\bauthor{\binits{Y.}~\bsnm{Lai}},
\bauthor{\binits{V.}~\bsnm{Simonyan}} and
\bauthor{\binits{R.}~\bsnm{Mazumder}},
\batitle{Enabling precision medicine via standard communication of {HTS}
provenance, analysis, and results},
\bjtitle{PLOS Biology}
\bvolume{16}(\bissue{12})
(\byear{2018}),
\bnumber{e3000099}.
\bid{doi={10.1371/journal.pbio.3000099}}
\end{barticle}
%
\OrigBibText
G.~Alterovitz,
D.~Dean,
C.~Goble,
M.R.~Crusoe,
S.~Soiland-Reyes,
A.~Bell,
A.~Hayes,
A.~Suresh,
A.~Purkayastha,
C.H.~King,
D.~Taylor,
E.~Johanson,
E.E.~Thompson,
E.~Donaldson,
H.~Morizono,
H.~Tsang,
J.K.~Vora,
J.~Goecks,
J.~Yao,
J.S.~Almeida,
J.~Keeney,
K.~Addepalli,
K.~Krampis,
K.M.~Smith,
L.~Guo,
M.~Walderhaug,
M.~Schito,
M.~Ezewudo,
N.~Guimera,
P.~Walsh,
R.~Kahsay,
S.~Gottipati,
T.C.~Rodwell,
T.~Bloom,
Y.~Lai,
V.~Simonyan and
R.~Mazumder,
\textit{Enabling precision medicine via standard communication of {HTS}
provenance, analysis, and results.},
{PLOS} Biology
16(12)
(2018),
e3000099.
doi:10.1371/journal.pbio.3000099.
\endOrigBibText
\bptok{structpyb}
\endbibitem

@@

%b10 ###bbsrt2
%b64 ###
\bibitem{doi:10.1371/journal.ppat.1008643}
%
\begin{barticle}
\bauthor{\binits{D.}~\bsnm{Baker}},
\bauthor{\binits{M.}~\bsnm{van den Beek}},
\bauthor{\binits{D.}~\bsnm{Blankenberg}},
\bauthor{\binits{D.}~\bsnm{Bouvier}},
\bauthor{\binits{J.}~\bsnm{Chilton}},
\bauthor{\binits{N.}~\bsnm{Coraor}},
\bauthor{\binits{F.}~\bsnm{Coppens}},
\bauthor{\binits{I.}~\bsnm{Eguinoa}},
\bauthor{\binits{S.}~\bsnm{Gladman}},
\bauthor{\binits{B.}~\bsnm{Gr\"{u}ning}},
\bauthor{\binits{N.}~\bsnm{Keener}},
\bauthor{\binits{D.}~\bsnm{Larivi\`{e}re}},
\bauthor{\binits{A.}~\bsnm{Lonie}},
\bauthor{\binits{S.}~\bsnm{Kosakovsky Pond}},
\bauthor{\binits{W.}~\bsnm{Maier}},
\bauthor{\binits{A.}~\bsnm{Nekrutenko}},
\bauthor{\binits{J.}~\bsnm{Taylor}} and
\bauthor{\binits{S.}~\bsnm{Weaver}},
\batitle{No more business as usual: Agile and effective responses to emerging
pathogen threats require open data and open analytics},
\bjtitle{PLOS Pathogens}
\bvolume{16}(\bissue{8})
(\byear{2020}),
\bnumber{e1008643}.
\bid{doi={10.1371/journal.ppat.1008643}}
\end{barticle}
%
\OrigBibText
D.~Baker,
M.~van~den Beek,
D.~Blankenberg,
D.~Bouvier,
J.~Chilton,
N.~Coraor,
F.~Coppens,
I.~Eguinoa,
S.~Gladman,
B.~Gr\"{u}ning,
N.~Keener,
D.~Larivi\`{e}re,
A.~Lonie,
S.~Kosakovsky~Pond,
W.~Maier,
A.~Nekrutenko,
J.~Taylor and
S.~Weaver,
\textit{No more business as usual: Agile and effective responses to emerging
pathogen threats require open data and open analytics.},
{PLOS} Pathogens
16(8)
(2020),
e1008643.
doi:10.1371/journal.ppat.1008643.
\endOrigBibText
\bptok{structpyb}
\endbibitem

%b11 ###bbsrt2
%b89 ###
\bibitem{doi:10.5334/dsj-2019-044}
%
\begin{barticle}
\bauthor{\binits{M.}~\bsnm{Barker}},
\bauthor{\binits{R.}~\bsnm{Wilkinson}} and
\bauthor{\binits{A.}~\bsnm{Treloar}},
\batitle{The Australian Research Data Commons},
\bjtitle{Data Science Journal}
\bvolume{18}
(\byear{2019}).
\bid{doi={10.5334/dsj-2019-044}}
\end{barticle}
%
\OrigBibText
M.~Barker,
R.~Wilkinson and
A.~Treloar,
The Australian Research Data Commons,
\textit{Data Science Journal}
\textbf{18}
(2019), 00.
doi:10.5334/dsj-2019-044.
\endOrigBibText
\bptok{structpyb}
\endbibitem

@@

%b14 ###bbsrt2
%b12 ###
\bibitem{doi:10.1016/j.websem.2015.01.003}
%
\begin{barticle}
\bauthor{\binits{K.}~\bsnm{Belhajjame}},
\bauthor{\binits{J.}~\bsnm{Zhao}},
\bauthor{\binits{D.}~\bsnm{Garijo}},
\bauthor{\binits{M.}~\bsnm{Gamble}},
\bauthor{\binits{K.}~\bsnm{Hettne}},
\bauthor{\binits{R.}~\bsnm{Palma}},
\bauthor{\binits{E.}~\bsnm{Mina}},
\bauthor{\binits{O.}~\bsnm{Corcho}},
\bauthor{\binits{J.M.}~\bsnm{G\'{o}mez-P\'{e}rez}},
\bauthor{\binits{S.}~\bsnm{Bechhofer}},
\bauthor{\binits{G.}~\bsnm{Klyne}} and
\bauthor{\binits{C.}~\bsnm{Goble}},
\batitle{Using a suite of ontologies for preserving workflow-centric
research objects},
\bjtitle{Web Semantics: Science, Services and Agents on the World Wide Web}
\bvolume{32}
(\byear{2015}),
\bfpage{16}--\blpage{42}.
\bid{doi={10.1016/j.websem.2015.01.003}}
\end{barticle}
%
\OrigBibText
K.~Belhajjame,
J.~Zhao,
D.~Garijo,
M.~Gamble,
K.~Hettne,
R.~Palma,
E.~Mina,
O.~Corcho,
J.M.~G\'{o}mez-P\'{e}rez,
S.~Bechhofer,
G.~Klyne and
C.~Goble,
\textit{Using a suite of ontologies for preserving workflow-centric research
objects},
Web Semantics: Science, Services and Agents on the World Wide Web
32
(2015),
16--42.
doi:10.1016/j.websem.2015.01.003.
\endOrigBibText
\bptok{structpyb}
\endbibitem

@@

%b32 ###bbsrt2
%b92 ###
\bibitem{doi:10.1045/january2011-crosas}
%
\begin{barticle}
\bauthor{\binits{M.}~\bsnm{Crosas}},
\batitle{The DataVerse Network: An open-source application for sharing,
discovering and preserving data},
\bjtitle{D-Lib Magazine}
\bvolume{17}(\bissue{1/2})
(\byear{2011}).
\bid{doi={10.1045/january2011-crosas}}
\end{barticle}
%
\OrigBibText
M.~Crosas,
The Dataverse Network: An Open-Source Application for Sharing,
Discovering and
Preserving Data,
\textit{D-Lib Magazine}
\textbf{17}(1/2)
(2011)
00.
doi:10.1045/january2011-crosas.
\endOrigBibText
\bptok{structpyb}
\endbibitem

@@

%b36 ###bbsrt2
%b69 ###
\bibitem{doi:10.1145/3486897}
%
\begin{bbook}
\bauthor{\binits{M.R.}~\bsnm{Crusoe}},
\bauthor{\binits{S.}~\bsnm{Abeln}},
\bauthor{\binits{A.}~\bsnm{Iosup}},
\bauthor{\binits{P.}~\bsnm{Amstutz}},
\bauthor{\binits{J.}~\bsnm{Chilton}},
\bauthor{\binits{N.}~\bsnm{Tijani\'{c}}},
\bauthor{\binits{H.}~\bsnm{M\'{e}nager}},
\bauthor{\binits{S.}~\bsnm{Soiland-Reyes}} and
\bauthor{\binits{C.}~\bsnm{Goble}},
\bbtitle{Methods Included: Standardizing Computational Reuse and Portability
with the Common Workflow Language},
\bpublisher{Communications of the ACM},
\byear{2022}.
\bcomment{Accepted}.
\bid{doi={10.1145/3486897}}
\end{bbook}
%
\OrigBibText
M.R.~Crusoe,
S.~Abeln,
A.~Iosup,
P.~Amstutz,
J.~Chilton,
N.~Tijani\'{c},
H.~M\'{e}nager,
S.~Soiland-Reyes and
C.~Goble,
\textit{Methods Included: Standardizing Computational Reuse and Portability
with the Common Workflow Language},
Communications of the ACM
(2022),
Accepted.
doi:10.1145/3486897.
\endOrigBibText
\bptok{structpyb}
\endbibitem

@@

%b91 ###bbsrt2
%b6 ###
\bibitem{isbn:9781315351148}
%
\begin{botherref}
\oauthor{\binits{B.}~\bsnm{Mons}},
Data Stewardship for Open Science,
1st edn,
Taylor \& Francis,
p.~240.
ISBN \bisbn{9781315351148}.
\end{botherref}
%
\OrigBibText
B.~Mons,
\textit{Data Stewardship for Open Science},
1st edn,
Taylor \& Francis,
p.~240.
ISBN 9781315351148.
\endOrigBibText
\bptok{structpyb}
\endbibitem
